Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-28 manuscript.Rmd
Update primary figure paths

```{r plot-RR-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.'}

# call image
knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_all_RR.png")

```{r plot-DET-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.'}

# call image
knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_all_DET.png")

```{r plot-RR-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.'}

# call image
knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_pos_RR.png")

```{r plot-DET-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.'}

# call image
knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_pos_DET.png")

```{r plot-RR-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.'}

# call image
knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_neg_RR.png")

```{r plot-DET-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.'}

# call image
knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_neg_DET.png")

@@

```{r plot-RR-source-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_all_RR.png")

```{r plot-DET-source-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_all_DET.png")

```{r plot-RR-source-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_pos_RR.png")

```{r plot-DET-source-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_pos_DET.png")

```{r plot-RR-source-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_neg_RR.png")

```{r plot-DET-source-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_neg_DET.png")

>>>>

```{r plot-wcrqa-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA for social cohesion and event counts from target filtered data.', out.extra='angle=90'}

# call image
knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_all.png")

@@

```{r plot-wcrqa-source-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA for social cohesion and event counts from source and target filtered data.', out.extra='angle=90'}

# call image
knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_all.png")

### 2020-05-28 manuscript.tex
Update primary figure paths

\begin{figure}
\includegraphics[width=4in]{./results/primary/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/primary/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/primary/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/primary/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/primary/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/primary/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg}
\end{figure}

@@

\begin{figure}
\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg}
\end{figure}

@@

@@

\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-Phoenix}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-Phoenix}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-icews}
\end{figure}
\begin{figure}
\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-icews}
\end{figure}
\end{appendix}

>>>>

\begin{figure}
\includegraphics[width=9in,angle=90]{./results/primary/windowed-crqa/target-windowed_all} \caption{Windowed CRQA for social cohesion and event counts from target filtered data.}\label{fig:plot-wcrqa-targ-all}
\end{figure}

@@

\begin{figure}
\includegraphics[width=9in,angle=90]{./results/primary/windowed-crqa/source_target-windowed_all} \caption{Windowed CRQA for social cohesion and event counts from source and target filtered data.}\label{fig:plot-wcrqa-source-targ-all}
\end{figure}

@@

\begin{verbatim}
## Warning in readLines(x, encoding = "UTF-8"): incomplete final line found on
## 'appendix.Rmd'
\end{verbatim}

@@

\begin{figure}
\includegraphics[width=0.9\linewidth,angle=90]{./results/secondary/phoenix/windowed-crqa/target-windowed_all} \caption{Windowed CRQA for social cohesion and event counts from target filtered data.}\label{fig:plot-secondary-phoenix-wcrqa-targ-all}
\end{figure}

\begin{figure}
\includegraphics[width=0.9\linewidth,angle=90]{./results/secondary/phoenix/windowed-crqa/source_target-windowed_all} \caption{Windowed CRQA for social cohesion and event counts from target filtered data.}\label{fig:plot-secondary-phoenix-wcrqa-source-targ-all}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.9\linewidth,angle=90]{./results/secondary/icews/windowed-crqa/target-windowed_all} \caption{Windowed CRQA for social cohesion and event counts from target filtered data.}\label{fig:plot-secondary-icews-wcrqa-targ-all}
\end{figure}

\begin{figure}
\includegraphics[width=0.9\linewidth,angle=90]{./results/secondary/icews/windowed-crqa/source_target-windowed_all} \caption{Windowed CRQA for social cohesion and event counts from target filtered data.}\label{fig:plot-secondary-icews-wcrqa-source-targ-all}
\end{figure}
\end{appendix}
